Assessing exposure to Atlantic Basin tropical storms in United States counties

### 2016-06-13 writing/DraftExposurePaper/DraftExposurePaper.Rmd
made two quick spelling edits

---
title: Assessing exposure to Atlantic Basin tropical storms in United States counties
author:
  - name: Joshua Ferreri
    email: alice@example.com
    affiliation: Colorado State University
  - name: Meilin Yan
    email: alice@example.com
    affiliation: Colorado State University
  - name: Mohammad Z. Al-Hamdan
    email: alice@example.com
    affiliation: NASA Marshall Space Flight Center
  - name: William L. Crosson
    email: alice@example.com
    affiliation: NASA Marshall Space Flight Center
  - name: Seth Guikema
    email: alice@example.com
    affiliation: University of Michigan
  - name: Roger D. Peng
    email: alice@example.com
    affiliation: Johns Hopkins Bloomberg School of Public Health
  - name: G. Brooke Anderson
    email: brooke.anderson@colostate.edu
    affiliation: Colorado State University
    footnote: Corresponding Author
address:
  - code: Colorado State University
    address: Department of Environmental and Radiological Health Sciences, Lake Street, Fort Collins, CO, Zip
  - code: NASA Marshall Space Flight Center
    address: Universities Space Research Association, Street, Huntsville, AL, Zip
  - code: University of Michigan
    address: Department, Street, City, State, Zip
  - code: Johns Hopkins Bloomberg School of Public Health
    address: Department of Biostatistics, Street, Baltimore, MD, Zip
abstract: |
  There are many important applications for having county-level estimates of exposure to tropical storms over many years. For example, ... . Current approaches include ... but have the following limitations ... .

@@

It can be very difficult to reliabily measure rain during extreme rain events, including tropical storms. For example, a heavy rain can wash away [?] rain monitors [?]. It can also be very hard to measure rain during heavy wind, as the rain does not fall straight into the monitor [?].

>>>>

---
title: Assessing exposure to Atlantic Basin tropical storms in United States counties
author:
  - name: Joshua Ferreri
    email: joshua.m.ferreri@gmail.com
    affiliation: Colorado State University
  - name: Meilin Yan
    email: alice@example.com
    affiliation: Colorado State University
  - name: Mohammad Z. Al-Hamdan
    email: alice@example.com
    affiliation: NASA Marshall Space Flight Center
  - name: William L. Crosson
    email: alice@example.com
    affiliation: NASA Marshall Space Flight Center
  - name: Seth Guikema
    email: alice@example.com
    affiliation: University of Michigan
  - name: Roger D. Peng
    email: alice@example.com
    affiliation: Johns Hopkins Bloomberg School of Public Health
  - name: G. Brooke Anderson
    email: brooke.anderson@colostate.edu
    affiliation: Colorado State University
    footnote: Corresponding Author
address:
  - code: Colorado State University
    address: Department of Environmental and Radiological Health Sciences, Lake Street, Fort Collins, CO, Zip
  - code: NASA Marshall Space Flight Center
    address: Universities Space Research Association, Street, Huntsville, AL, Zip
  - code: University of Michigan
    address: Department, Street, City, State, Zip
  - code: Johns Hopkins Bloomberg School of Public Health
    address: Department of Biostatistics, Street, Baltimore, MD, Zip
abstract: |
  There are many important applications for having county-level estimates of exposure to tropical storms over many years. For example, ... . Current approaches include ... but have the following limitations ... .

@@

It can be very difficult to reliably measure rain during extreme rain events, including tropical storms. For example, a heavy rain can wash away [?] rain monitors [?]. It can also be very hard to measure rain during heavy wind, as the rain does not fall straight into the monitor [?].
